---
title: "MLB Attendance Project - Models"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Dependencies
```{r}
library(tidyverse)
library(sjPlot)
#if newer features are required, use the following to install sjPlot and all dependencies
#devtools::install_github("strengejacke/strengejacke")
```


Load Data
```{r}
attendanceTicketPriceWAR <- read.csv("data/attendanceTicketPriceWAR.csv")
attendanceTicketPriceWAR$mowar2 <- attendanceTicketPriceWAR$mowar * attendanceTicketPriceWAR$mowar
attendanceTicketPriceWAR$numTeamWins2 <- attendanceTicketPriceWAR$numTeamWins * attendanceTicketPriceWAR$numTeamWins
attendanceTicketPriceWAR$winDifference <- attendanceTicketPriceWAR$Win - attendanceTicketPriceWAR$WinExpectation 
attendanceTicketPriceWAR$VegasWins <- attendanceTicketPriceWAR$WinExpectation
```



1) Original
pWAR, dWAR, and moWAR Models
```{r}
#attendance= b0 + b1*oWAR + b2*pWAR + b3*dWAR + b4*luckyWins + team fixed effects
attendanceWARModel1 <- lm(data = attendanceTicketPriceWAR,
                       Attendance ~
                         mowar +
                         pwar +
                         dwar +
                         LuckyWins + 
                         factor(Team))
print("attendanceWARModel1")
summary(attendanceWARModel1)


#attendance= b0 + b1*oWAR + b2*pWAR + b3*dWAR + b4*luckyWins + b5*MSA per capita gross metro product + b6*MSA population + team fixed effects
attendanceWARModel2 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    mowar +
    pwar +
    dwar +
    LuckyWins + 
    gdppercapita +
    gdppercapita2 +
    Population +
    factor(Team)
)
print("attendanceWARModel2")
summary(attendanceWARModel2)



#attendance= b0 + b1*oWAR + b2*pWAR + b3*dWAR + b4*luckyWins + b5*MSA per capita gross metro product + b6*MSA population +  b7*avg_price + b8*attendance growth + b9*made the playoffs + b10*change in win% + new stadium effects + team fixed effects
attendanceWARModel3 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    mowar +
    pwar +
    dwar +
    LuckyWins + 
    gdppercapita +
    gdppercapita2 +
    Population +
    DeltaLeagueAttendanceMinusTeam +
    PlayedInPlayoffs +
    DeltaWL +
    NewStadium +
    factor(Team)
)
print("attendanceWARModel3")
summary(attendanceWARModel3)

attendanceDeltaWARModel3_1 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    Win +
    deltaMOWAR +
    deltaDWAR +
    deltaPWAR +
    deltaLuckyWins +
    AveragePrice +
    gdppercapita +
    gdppercapita2 +
    Population +
    DeltaLeagueAttendanceMinusTeam +
    PlayedInPlayoffs +
    NewStadium +
    factor(Team)
)
print("attendanceDeltaWARModel3_1")
summary(attendanceDeltaWARModel3_1)

attendanceDeltaWARModel3_2 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    VegasWins +
    deltaMOWAR +
    deltaDWAR +
    deltaPWAR +
    deltaLuckyWins +
    gdppercapita +
    gdppercapita2 +
    Population +
    DeltaLeagueAttendanceMinusTeam +
    PlayedInPlayoffs +
    NewStadium +
    factor(Team)
)
print("attendanceDeltaWARModel3_2")
summary(attendanceDeltaWARModel3_2)


oWARModel <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    mowar
)
print("oWARModel")
summary(oWARModel)

dWARModel <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    dwar
)
print("dWARModel")
summary(dWARModel)

pWARModel <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    pwar
)
print("pWARModel")
summary(pWARModel)

```






oWAR/total WAR + pWAR/total WAR models:
```{r}
#attendance= b0 + b1*oWAR/total WAR + b2*pWAR/total WAR + b3*numTeamWins + team fixed effects
attendanceWARProportionModel1 <- lm(data = attendanceTicketPriceWAR,
                       Attendance ~
                         mowarOverWar +
                         pwarOverWar +
                         numTeamWins +
                         factor(Team))
print("attendanceWARProportionModel1")
summary(attendanceWARProportionModel1)


#attendance= b0 + b1*oWAR/total WAR + b2*pWAR/total WAR + b3*NumWins + b4*MSA per capita gross metro product + b5*MSA population + team fixed effects
attendanceWARProportionModel2 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    mowarOverWar +
    pwarOverWar +
    numTeamWins +
    gdppercapita +
    gdppercapita2 +
    Population +
    factor(Team)
)
print("attendanceWARProportionModel2")
summary(attendanceWARProportionModel2)


#attendance= b0 + b1*NumWins + b2*MSA per capita gross metro product + b3*MSA population +  b4*avg_price + b5*attendance growth + b6*made the playoffs + b7*change in win% + new stadium effects + team fixed effects 
attendanceWARProportionModel3Base <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    VegasWins +
    gdppercapita +
    gdppercapita2 +
    Population +
    DeltaLeagueAttendanceMinusTeam +
    PlayedInPlayoffs +
    DeltaWL +
    NewStadium +
    factor(Team)
)
print("attendanceWARProportionModel3Base")
summary(attendanceWARProportionModel3Base)
attendanceTicketPriceWAR$TeamWins <- attendanceTicketPriceWAR$numTeamWins
attendanceWARProportionModel3BaseActualWins <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    TeamWins +
    gdppercapita +
    gdppercapita2 +
    Population +
    DeltaLeagueAttendanceMinusTeam +
    PlayedInPlayoffs +
    DeltaWL +
    NewStadium +
    factor(Team)
)
print("attendanceWARProportionModel3BaseActualWins")
summary(attendanceWARProportionModel3BaseActualWins)


#attendance= b0 + b1*oWAR/total WAR + b2*pWAR/total WAR + b3*NumWins + b4*MSA per capita gross metro product + b5*MSA population +  b6*avg_price + b7*attendance growth + b8*made the playoffs + b9*change in win% + new stadium effects + team fixed effects
attendanceWARProportionModel3 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    mowarOverWar +
    pwarOverWar +
    VegasWins +
    gdppercapita +
    gdppercapita2 +
    Population +
    DeltaLeagueAttendanceMinusTeam +
    PlayedInPlayoffs +
    DeltaWL +
    NewStadium +
    factor(Team)
)
print("attendanceWARProportionModel3")
summary(attendanceWARProportionModel3)

attendanceWARProportionModel3ActualWins <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    mowarOverWar +
    pwarOverWar +
    TeamWins +
    gdppercapita +
    gdppercapita2 +
    Population +
    DeltaLeagueAttendanceMinusTeam +
    PlayedInPlayoffs +
    DeltaWL +
    NewStadium +
    factor(Team)
)
print("attendanceWARProportionModel3ActualWins")
summary(attendanceWARProportionModel3ActualWins)

```


2) Time Dummies
pWAR, dWAR, and moWAR Models
```{r}
#attendance= b0 + b1*oWAR + b2*pWAR + b3*dWAR + b4*luckyWins + team fixed effects + season fixed effects
attendanceWARTDModel1 <- lm(data = attendanceTicketPriceWAR,
                       Attendance ~
                         mowar +
                         pwar +
                         dwar +
                         LuckyWins + 
                         factor(Team) +
                         factor(Season))
print("attendanceWARTDModel1")
summary(attendanceWARTDModel1)


#attendance= b0 + b1*oWAR + b2*pWAR + b3*dWAR + b4*luckyWins + b5*MSA per capita gross metro product + b6*MSA population + team fixed effects + season fixed effects
attendanceWARTDModel2 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    mowar +
    pwar +
    dwar +
    LuckyWins + 
    gdppercapita +
    gdppercapita2 +
    Population +
    factor(Team) +
    factor(Season)
)
print("attendanceWARTDModel2")
summary(attendanceWARTDModel2)

#attendance= b0 + b1*oWAR + b2*pWAR + b3*dWAR + b4*luckyWins + b5*MSA per capita gross metro product + b6*MSA population +  b7*avg_price + b8*attendance growth + b9*made the playoffs + b10*change in win% + new stadium effects + team fixed effects + season fixed effects
attendanceWARTDModel3 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    mowar +
    pwar +
    dwar +
    LuckyWins + 
    gdppercapita +
    gdppercapita2 +
    Population +
    DeltaLeagueAttendanceMinusTeam +
    PlayedInPlayoffs +
    DeltaWL +
    NewStadium +
    factor(Team) +
    factor(Season)
)
print("attendanceWARTDModel3")
summary(attendanceWARTDModel3)

```






oWAR/total WAR + pWAR/total WAR models:
```{r}
#attendance= b0 + b1*oWAR/total WAR + b2*pWAR/total WAR + b3*NumWins + team fixed effects + season fixed effects
attendanceWARTDProportionModel1 <- lm(data = attendanceTicketPriceWAR,
                       Attendance ~
                         mowarOverWar +
                         pwarOverWar +
                         numTeamWins +
                         factor(Team) +
                         factor(Season))
print("attendanceWARTDProportionModel1")
summary(attendanceWARTDProportionModel1)


#attendance= b0 + b1*oWAR/total WAR + b2*pWAR/total WAR + b3*NumWins + b4*MSA per capita gross metro product + b5*MSA population + team fixed effects + season fixed effects
attendanceWARTDProportionModel2 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    mowarOverWar +
    pwarOverWar +
    numTeamWins +
    gdppercapita +
    gdppercapita2 +
    Population +
    factor(Team) +
    factor(Season)
)
print("attendanceWARTDProportionModel2")
summary(attendanceWARTDProportionModel2)

#attendance= b0 + b1*oWAR/total WAR + b2*pWAR/total WAR + b3*NumWins + b4*MSA per capita gross metro product + b5*MSA population +  b6*avg_price + b7*attendance growth + b8*made the playoffs + b9*change in win% + new stadium effects + team fixed effects + season fixed effects
attendanceWARTDProportionModel3 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    mowarOverWar +
    pwarOverWar +
    numTeamWins +
    gdppercapita +
    gdppercapita2 +
    Population +
    DeltaLeagueAttendanceMinusTeam +
    PlayedInPlayoffs +
    DeltaWL +
    NewStadium +
    factor(Team) +
    factor(Season)
)
print("attendanceWARTDProportionModel3")
summary(attendanceWARTDProportionModel3)

```



3) Time Trend
pWAR, dWAR, and moWAR Models
```{r}
#attendance= b0 + b1*oWAR + b2*pWAR + b3*dWAR +season +  team fixed effects
attendanceWARTTrendModel1 <- lm(data = attendanceTicketPriceWAR,
                       Attendance ~
                         mowar +
                         pwar +
                         dwar +
                         LuckyWins + 
                         Season +
                         factor(Team))
print("attendanceWARTTrendModel1")
summary(attendanceWARTTrendModel1)


#attendance= b0 + b1*oWAR + b2*pWAR + b3*dWAR + b4*luckyWins + b5*MSA per capita gross metro product + b6*MSA population + season +  team fixed effects 
attendanceWARTTrendModel2 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    mowar +
    pwar +
    dwar +
    LuckyWins + 
    gdppercapita +
    gdppercapita2 +
    Population +
    Season+
    factor(Team)
)
print("attendanceWARTTrendModel2")
summary(attendanceWARTTrendModel2)



#attendance= b0 + b1*oWAR + b2*pWAR + b3*dWAR + b4*luckyWins + b5*MSA per capita gross metro product + b6*MSA population +  b7*avg_price + b8*attendance growth + b9*made the playoffs + b10*change in win% + new stadium effects + season + team fixed effects
attendanceWARTTrendModel3 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    mowar +
    pwar +
    dwar +
    LuckyWins + 
    gdppercapita +
    gdppercapita2 +
    Population +
    DeltaLeagueAttendanceMinusTeam +
    PlayedInPlayoffs +
    DeltaWL +
    NewStadium +
    Season+
    factor(Team)
)
print("attendanceWARTTrendModel3")
summary(attendanceWARTTrendModel3)

#attendance= b0 + b2*numTeamWins + b3*MSA per capita gross metro product + b4*MSA population +  b5*avg_price + b6*attendance growth + b7*made the playoffs + b8*change in win% + new stadium effects + season + team fixed effects
attendanceWARTTrendModel4 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    numTeamWins +
    gdppercapita +
    gdppercapita2 +
    Population +
    DeltaLeagueAttendanceMinusTeam +
    PlayedInPlayoffs +
    DeltaWL +
    NewStadium +
    Season+
    factor(Team)
)
print("attendanceWARTTrendModel4")
summary(attendanceWARTTrendModel4)

```






oWAR/total WAR + pWAR/total WAR models:
```{r}
#attendance= b0 + b1*oWAR/total WAR + b2*pWAR/total WAR + b3*NumWins + season + team fixed effects 
attendanceWARTTrendProportionModel1 <- lm(data = attendanceTicketPriceWAR,
                       Attendance ~
                         mowarOverWar +
                         pwarOverWar +
                         numTeamWins +
                         Season +
                         factor(Team))
print("attendanceWARTTrendProportionModel1")
summary(attendanceWARTTrendProportionModel1)


#attendance= b0 + b1*oWAR/total WAR + b2*pWAR/total WAR + b3*NumWins + b4*MSA per capita gross metro product + b5*MSA population + season + team fixed effects
attendanceWARTTrendProportionModel2 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    mowarOverWar +
    pwarOverWar +
    numTeamWins +
    gdppercapita +
    gdppercapita2 +
    Population +
    Season+
    factor(Team)
)
print("attendanceWARTTrendProportionModel2")
summary(attendanceWARTTrendProportionModel2)

#attendance= b0 + b1*NumWins + b2*MSA per capita gross metro product + b3*MSA population +  b4*avg_price + b5*attendance growth + b6*made the playoffs + b7*change in win% + new stadium effects + season + team fixed effects 
attendanceWARTTrendProportionModel3Base <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    numTeamWins +
    gdppercapita +
    gdppercapita2 +
    Population +
    DeltaLeagueAttendanceMinusTeam +
    PlayedInPlayoffs +
    DeltaWL +
    NewStadium +
    Season+
    factor(Team)
)
print("attendanceWARTTrendProportionModel3Base")
summary(attendanceWARTTrendProportionModel3Base)

#attendance= b0 + b1*oWAR/total WAR + b2*pWAR/total WAR + b3*NumWins + b4*MSA per capita gross metro product + b5*MSA population +  b6*avg_price + b7*attendance growth + b8*made the playoffs + b9*change in win% + new stadium effects + season + team fixed effects
attendanceWARTTrendProportionModel3 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    mowarOverWar +
    pwarOverWar +
    numTeamWins +
    gdppercapita +
    gdppercapita2 +
    Population +
    
    DeltaLeagueAttendanceMinusTeam +
    PlayedInPlayoffs +
    DeltaWL +
    NewStadium +
    Season+
    factor(Team)
)
print("attendanceWARTTrendProportionModel3")
summary(attendanceWARTTrendProportionModel3)

```


4) Time Dummies and Time Trend
pWAR, dWAR, and moWAR Models
```{r}
#attendance= b0 + b1*oWAR + b2*pWAR + b3*dWAR + b4*luckyWins + season + team fixed effects + season fixed effects
attendanceWARTDTTrendModel1 <- lm(data = attendanceTicketPriceWAR,
                       Attendance ~
                         mowar +
                         pwar +
                         dwar +
                         LuckyWins + 
                         Season+
                         factor(Team) +
                         factor(Season))
print("attendanceWARTDTTrendModel1")
summary(attendanceWARTDTTrendModel1)


#attendance= b0 + b1*oWAR + b2*pWAR + b3*dWAR + b4*luckyWins + b5*MSA per capita gross metro product + b6*MSA population + season + team fixed effects + season fixed effects
attendanceWARTDTTrendModel2 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    mowar +
    pwar +
    dwar +
    LuckyWins + 
    gdppercapita +
    gdppercapita2 +
    Population +
    Season+
    factor(Team) +
    factor(Season)
)
print("attendanceWARTDTTrendModel2")
summary(attendanceWARTDTTrendModel2)

#attendance= b0 + b1*oWAR + b2*pWAR + b3*dWAR + b4*luckyWins + b5*MSA per capita gross metro product + b6*MSA population +  b7*avg_price + b8*attendance growth + b9*made the playoffs + b10*change in win% + new stadium effects + season + team fixed effects + season fixed effects
attendanceWARTDTTrendModel3 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    mowar +
    pwar +
    dwar +
    LuckyWins + 
    gdppercapita +
    gdppercapita2 +
    Population +
    DeltaLeagueAttendanceMinusTeam +
    PlayedInPlayoffs +
    DeltaWL +
    NewStadium +
    Season+
    factor(Team) +
    factor(Season)
)
print("attendanceWARTDTTrendModel3")
summary(attendanceWARTDTTrendModel3)

```






oWAR/total WAR + pWAR/total WAR models:
```{r}
#attendance= b0 + b1*oWAR/total WAR + b2*pWAR/total WAR + b3*NumWins + season + team fixed effects + season fixed effects
attendanceWARTDTTrendProportionModel1 <- lm(data = attendanceTicketPriceWAR,
                       Attendance ~
                         mowarOverWar +
                         pwarOverWar +
                         numTeamWins +
                         Season+
                         factor(Team) +
                         factor(Season))
print("attendanceWARTDTTrendProportionModel1")
summary(attendanceWARTDTTrendProportionModel1)


#attendance= b0 + b1*oWAR/total WAR + b2*pWAR/total WAR + b3*NumWins + b4*MSA per capita gross metro product + b5*MSA population + season + team fixed effects + season fixed effects
attendanceWARTDTTrendProportionModel2 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    mowarOverWar +
    pwarOverWar +
    numTeamWins +
    gdppercapita +
    gdppercapita2 +
    Population +
    Season+
    factor(Team) +
    factor(Season)
)
print("attendanceWARTDTTrendProportionModel2")
summary(attendanceWARTDTTrendProportionModel2)


#attendance= b0 + b1*NumWins + b2*MSA per capita gross metro product + b3*MSA population +  b4*avg_price + b5*attendance growth + b6*made the playoffs + b7*change in win% + new stadium effects + season + team fixed effects + season fixed effects
attendanceWARTDTTrendProportionModel3Base <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    numTeamWins +
    gdppercapita +
    gdppercapita2 +
    Population +
    DeltaLeagueAttendanceMinusTeam +
    PlayedInPlayoffs +
    DeltaWL +
    NewStadium +
    Season+
    factor(Team) +
    factor(Season)
)
print("attendanceWARTDTTrendProportionModel3Base")
summary(attendanceWARTDTTrendProportionModel3Base)


#attendance= b0 + b1*oWAR/total WAR + b2*pWAR/total WAR + b3*NumWins + b4*MSA per capita gross metro product + b5*MSA population +  b6*avg_price + b7*attendance growth + b8*made the playoffs + b9*change in win% + new stadium effects + season + team fixed effects + season fixed effects
attendanceWARTDTTrendProportionModel3 <- lm(
  data = attendanceTicketPriceWAR,
  Attendance ~
    mowarOverWar +
    pwarOverWar +
    numTeamWins +
    gdppercapita +
    gdppercapita2 +
    Population +
    DeltaLeagueAttendanceMinusTeam +
    PlayedInPlayoffs +
    DeltaWL +
    NewStadium +
    Season+
    factor(Team) +
    factor(Season)
)
print("attendanceWARTDTTrendProportionModel3")
summary(attendanceWARTDTTrendProportionModel3)



```



Prep for modeling
```{r}
#fixedEffects will contains all of the dummy variables that we don't want shown in the tables
fixedEffects <- c("factor(Season)20 [11,12,13,14,15,16,17,18,19]", "NewStadium [0,1,2,3,4,5,6,7,8]","NewStadiumNA",
                  "factor(Team)Atlanta Braves",
                  "factor(Team)Baltimore Orioles",
                  "factor(Team)Boston Red Sox",
                  "factor(Team)Chicago Cubs",
                  "factor(Team)Chicago White Sox",
                  "factor(Team)Cincinnati Reds",
                  "factor(Team)Cleveland Indians",
                  "factor(Team)Colorado Rockies",
                  "factor(Team)Detroit Tigers",
                  "factor(Team)Houston Astros",
                  "factor(Team)Kansas City Royals",
                  "factor(Team)Los Angeles Angels",
                  "factor(Team)Los Angeles Dodgers",
                  "factor(Team)Miami Marlins",
                  "factor(Team)Milwaukee Brewers",
                  "factor(Team)Minnesota Twins",
                  "factor(Team)New York Mets",
                  "factor(Team)New York Yankees",
                  "factor(Team)Oakland Athletics",
                  "factor(Team)Philadelphia Phillies",
                  "factor(Team)Pittsburgh Pirates",
                  "factor(Team)San Diego Padres",
                  "factor(Team)San Francisco Giants",
                  "factor(Team)Seattle Mariners",
                  "factor(Team)St. Louis Cardinals",
                  "factor(Team)Tampa Bay Rays",
                  "factor(Team)Texas Rangers",
                  "factor(Team)Washington Nationals",
                  "factor(Team)Toronto Blue Jays")
```




Full Tables
```{r}

tab_model(attendanceWARModel1, attendanceWARModel2, attendanceWARModel3, attendanceWARTDModel1, attendanceWARTDModel2, attendanceWARTDModel3, attendanceWARTTrendModel1, attendanceWARTTrendModel2,attendanceWARTTrendModel3,attendanceWARTTrendModel4,dv.labels = c("attendanceWARModel1","attendanceWARModel2","attendanceWARModel3","attendanceWARTDModel1","attendanceWARTDModel2","attendanceWARTDModel3","attendanceWARTTrendModel1","attendanceWARTTrendModel2","attendanceWARTTrendModel3","attendanceWARTTrendModel4","attendanceWARTDTTrendModel1","attendanceWARTDTTrendModel2","attendanceWARTDTTrendModel3"), rm.terms = fixedEffects)


tab_model(attendanceWARProportionModel1, attendanceWARProportionModel2, attendanceWARProportionModel3, attendanceWARTDProportionModel1, attendanceWARTDProportionModel2, attendanceWARTDProportionModel3, attendanceWARTTrendProportionModel1, attendanceWARTTrendProportionModel2,attendanceWARTTrendProportionModel3,dv.labels = c("attendanceWARProportionModel1","attendanceWARProportionModel2","attendanceWARProportionModel3","attendanceWARTDProportionModel1","attendanceWARTDProportionModel2","attendanceWARTDProportionModel3","attendanceWARTTrendProportionModel1","attendanceWARTTrendProportionModel2","attendanceWARTTrendProportionModel3","attendanceWARTDTTrendProportionModel1","attendanceWARTDTTrendProportionModel2","attendanceWARTDTTrendProportionModel3"), rm.terms = fixedEffects)

```


Correlations
```{r}
library(mctest)
library(corpcor)
library(GGally)




y <- attendanceTicketPriceWAR["Attendance"]
x <- attendanceTicketPriceWAR[c("mowar", "pwar", "dwar", "LuckyWins", "gdppercapita","Population", "DeltaLeagueAttendanceMinusTeam", "PlayedInPlayoffs", "DeltaWL", "NewStadium")]
x <- attendanceTicketPriceWAR[c("mowar", "pwar", "dwar","LuckyWins")]

omcdiag(x=x,y=y)
ggpairs(x)
cor2pcor(cov(x))
imcdiag(x=x,y=y, method = "CVIF") #CVIF method (Curto and Pinto, 2011 <doi: 10.1080/02664763.2010.505956>)



oWARdWARCorrelation <- cor.test(attendanceTicketPriceWAR$mowar, attendanceTicketPriceWAR$dwar, method = "pearson")
oWARdWARCorrelation


```


autocorrelation
```{r}
library(lmtest)
dwtest(attendanceWARModel3)
dwtest(attendanceWARProportionModel3Base)
dwtest(attendanceWARProportionModel3)

```



Paper Tables
```{r}



tab_model(attendanceWARProportionModel3BaseActualWins,attendanceWARProportionModel3ActualWins, attendanceWARModel3, dv.labels = c("Base","WAR Proportion", "WAR Decomposed"), rm.terms = fixedEffects, show.se = TRUE, show.ci = FALSE, digits = 3)

tab_model(attendanceWARProportionModel3Base,attendanceWARProportionModel3, attendanceDeltaWARModel3_2, dv.labels = c("Base","WAR Proportion", "WAR Components Change"), rm.terms = fixedEffects, show.se = TRUE, show.ci = FALSE, digits = 3)

```


Summary Tables
```{r}




variablesToSummarize <- c("Attendance","Win","gdppercapita","Population","DeltaLeagueAttendanceMinusTeam","PlayedInPlayoffs","DeltaWL","NewStadium","mowarOverWar","pwarOverWar","deltaLuckyWins","mowar","dwar","pwar","LuckyWins")

variablesToSummarizePublished <- c("Attendance","Wins","GDPPerCapita","Population","DeltaLeagueAttendance","PlayedInPlayoffs","DeltaWL","New Stadium","moWAR/WAR","pWAR/WAR","deltaLuckyWins","moWAR","dWAR","pWAR","LuckyWins")

summaryStats <- data.frame()
for(i in 1:length(variablesToSummarize)){

  attendanceTicketPriceWAR %>% summarize_at(variablesToSummarize[i], funs(mean,sd,min,max,median), na.rm= TRUE) -> currentSummary
  currentSummary$Variable <- variablesToSummarizePublished[i]
  summaryStats %>% bind_rows(currentSummary) -> summaryStats
}

write_csv(summaryStats,path = "data/summaryStats.csv")

```

Suggestions
```{r}
summary(attendanceDeltaWARModel3_1)
summary(attendanceDeltaWARModel3_2)

summary(oWARModel)
summary(dWARModel)
summary(pWARModel)
```

Visualizations
```{r}
library(teamcolors)
library(cowplot)
library(ggpubr)

vegasOddsVActualWinsColor <- ggplot(attendanceTicketPriceWAR, aes(VegasWins, Win)) + geom_smooth(method="lm", se = FALSE, color="grey", linetype = 1, fullrange=TRUE) + geom_point(aes(color=Team,fill = Team),shape = 21, size = 3, stroke = 1) + scale_fill_teams(2) + scale_color_teams(1, guide = FALSE) + theme_minimal() + scale_x_continuous(limits=c(50, 110)) + scale_y_continuous(limits=c(50, 110)) +
theme(aspect.ratio=1)
vegasOddsVActualWinsColor

vegasOddsVActualWinsBW <- ggplot(attendanceTicketPriceWAR, aes(VegasWins, Win)) + geom_smooth(method="lm", se = FALSE, color="black", linetype = 1, fullrange=TRUE) + geom_point(shape = 21, size = 2, fill="black") + scale_fill_teams() + scale_color_teams(2, guide = FALSE) + theme_minimal() + scale_x_continuous(limits=c(50, 110)) + scale_y_continuous(limits=c(50, 110)) +
theme(aspect.ratio=1)+ scale_x_continuous(limits=c(50, 110)) + scale_y_continuous(limits=c(50, 110)) 
vegasOddsVActualWinsBW


mowarPlot <- ggplot(attendanceTicketPriceWAR, aes(mowar, Attendance)) + geom_smooth(method="lm", se = FALSE, color="grey", linetype = 1, fullrange=TRUE,formula = 'y ~ x') + geom_point(aes(color=Team,fill = Team),shape = 21, size = 3, stroke = 1) + scale_fill_teams(2) + scale_color_teams(1, guide = FALSE) + theme_minimal() +
theme(aspect.ratio=1)+ scale_x_continuous(limits=c(-12, 40)) + scale_y_continuous(limits=c(1200000, 3800000))
mowarPlot

pwarPlot <- ggplot(attendanceTicketPriceWAR, aes(pwar, Attendance)) + geom_smooth(method="lm", se = FALSE, color="grey", linetype = 1, fullrange=TRUE,formula = 'y ~ x') + geom_point(aes(color=Team,fill = Team),shape = 21, size = 3, stroke = 1) + scale_fill_teams(2) + scale_color_teams(1, guide = FALSE) + theme_minimal() +
theme(aspect.ratio=1)+ scale_x_continuous(limits=c(-12, 40)) + scale_y_continuous(limits=c(1200000, 3800000))
pwarPlot

dwarPlot <- ggplot(attendanceTicketPriceWAR, aes(dwar, Attendance)) + geom_smooth(method="lm", se = FALSE, color="grey", linetype = 1, fullrange=TRUE,formula = 'y ~ x') + geom_point(aes(color=Team,fill = Team),shape = 21, size = 3, stroke = 1) + scale_fill_teams(2) + scale_color_teams(1, guide = FALSE) + theme_minimal() +
theme(aspect.ratio=1)+ scale_x_continuous(limits=c(-12, 40)) + scale_y_continuous(limits=c(1200000, 3800000))
dwarPlot


ggarrange(mowarPlot, pwarPlot, dwarPlot + rremove("x.text"), 
          labels = c("moWAR","pWAR","dWAR"),
          ncol = 2, nrow = 2, align = "hv",
          common.legend = TRUE, legend="bottom")


```

